Place of death in NRS COVID-19 deaths: data processing for analysis, 2024 data

### 2024-02-02 covid_nrs_place_of_death_data_2024.Rmd
cursory update to change 2023 to 2024

---
title: "Place of death in NRS COVID-19 deaths: data processing for analysis, 2023 data"
author: "Jan Savinc"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
  code_folding: hide
toc: true
toc_float: true
editor_options: 
  chunk_output_type: console
---

@@

```{r}
## constants for use in graphs & annotations
weeks_available_2023 <- max(merged_deaths_overall$week_number[merged_deaths_overall$year==2023])
most_recent_date_available_2023 <- max(merged_deaths_overall$date_w_c)

earliest_date <- min(merged_deaths_overall$date_w_c)
current_year <- isoyear(most_recent_date_available_2023)

weeks_available_2023_disaggregated <- max(merged_deaths_age$week_number[merged_deaths_age$year==2023])
most_recent_date_available_2023_disaggregated <- max(merged_deaths_age$date_w_c)
```

@@

        period = glue::glue("Data from week 1, 2020 to week {weeks_available_2023}, 2022"),

@@

    ## 2023 data so far

@@

          year == 2023

@@

      period = glue::glue("2023, up to week {weeks_available_2023}"),

>>>>

---
title: "Place of death in NRS COVID-19 deaths: data processing for analysis, 2024 data"
author: "Jan Savinc"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
  code_folding: hide
toc: true
toc_float: true
editor_options: 
  chunk_output_type: console
---

@@

```{r}
## constants for use in graphs & annotations
weeks_available_2024 <- max(merged_deaths_overall$week_number[merged_deaths_overall$year==2024])
most_recent_date_available_2024 <- max(merged_deaths_overall$date_w_c)

earliest_date <- min(merged_deaths_overall$date_w_c)
current_year <- isoyear(most_recent_date_available_2024)

weeks_available_2024_disaggregated <- max(merged_deaths_age$week_number[merged_deaths_age$year==2024])
most_recent_date_available_2024_disaggregated <- max(merged_deaths_age$date_w_c)
```

@@

        period = glue::glue("Data from week 1, 2020 to week {weeks_available_2024}, 2022"),

@@

    ## 2024 data so far

@@

          year == 2024

@@

      period = glue::glue("2024, up to week {weeks_available_2024}"),
